dispRity manual

### 2019-03-06 inst/gitbook/index.Rmd
Updated 1.2.3

@@

 * The CRAN version is a more "strict" version of the package that does not include some functionalities such as this gitbook vignette because of compatibility issues with the CRAN requirement.
 * The GitHub version is a more "reactive" version (fed by user's suggestions and comments) and can contain more functionalities (see list below). This version exists on a `"release"` branch which is tested as strictly as the CRAN version with Travis and codecov. The `"master"` branch contains always the latest "piping hot", not yet release version. It might (though rarely) be bugged.

@@

@@

>>>>

Anyways to upload it, you can use

@@

 * The CRAN version is a more "strict" version of the package that does not include some functionalities (such as [`Claddis.ordination`](#Claddis-ordination) or this gitbook vignette) because of compatibility issues with the CRAN requirement.

 * The GitHub version is a more "reactive" version (fed by user's suggestions and comments) and can contain more functionalities (see list below). This version exists on a `"release"` branch which is tested as strictly as the CRAN version with Travis and codecov. The `"master"` branch contains always the latest "piping hot", not yet release version. It might (though rarely) be bugged.

<!-- badges out start 
[![Build Status](https://travis-ci.org/TGuillerme/dispRity.svg?branch=release)](https://travis-ci.org/TGuillerme/dispRity)
[![codecov](https://codecov.io/gh/TGuillerme/dispRity/branch/release/graph/badge.svg)](https://codecov.io/gh/TGuillerme/dispRity)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<-- badges out end   -->

@@

Functions not available on the CRAN version (`r version_CRAN`):

 * [`Claddis.ordination`](#Claddis-ordination)

@@

<!-- badges out start
 * The build status: [![Build Status](https://travis-ci.org/TGuillerme/dispRity.svg?branch=master)](https://travis-ci.org/TGuillerme/dispRity) which tests whether the package compiles (i.e. can be installed on your computer).
 * The code coverage: [![codecov](https://codecov.io/gh/TGuillerme/dispRity/branch/master/graph/badge.svg)](https://codecov.io/gh/TGuillerme/dispRity) which indicates the percentage of lines in the code that have been tested for expected behaviour.
 * The project status: [![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active) which indicates whether this package is maintained regularly or forgotten in the abyss of internet.
 * The development version: [![develVersion](https://img.shields.io/badge/devel%20version-1.2.1-green.svg?style=flat)](https://github.com/TGuillerme/dispRity) which indicates which version of the package you are about to install.

<-- badges out end   -->
